The transition redshift as a probe of reionization

### 2019-08-11 paper/ms.tex
Add beginning of OIII lum sec

@@

\section{Conclusions}

>>>>

\subsection{[\OIII] luminosity} \label{ssec:oiii_lum}

In order to model the relation between [\OIII] luminosity ($L_{\OIII}$) and
halo mass, we follow \citet{2019ApJ...874..133B}. Specifically, we assume that
the luminosity for halo $j$
\beq \label{eq:lum_mass_relation}
L_j(M) = L_0 \left[ \frac{M}{M_0} \right]^{\alpha} + s_j(w)
\eeq
where $L_0/M_0^{\alpha}$ is set to match the total average intensity of
[\OIII] at that redshift, $\alpha$ is the power-law index, and $s_j(w)$ is a
number randomly selected from a lognormal distribution with zero mean and
width $w$. Once the average intensity is fixed (which we assume so), this is a
two-parameter model ($\alpha$ and $w$) of the [\OIII] luminosity-mass
relation.

\section{Detectability}

@@

\section{Conclusions} \label{sec:conclusions}
